{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-20 thesis/education.tex
oops
some impact-on-grades revisions

{\bf Statistical significance.}
Table~\ref{tab:table-of-ze-studence} presents more detailed statistics from these six distributions.
To assess statistical significance,
% discrete == I used "version 2" of the AD metric that R outputs.
I use the $k$-sample discrete Anderson-Darling test \cite{anderson-darling}
provided by the R statistical programming environment \cite{r-lang,r-ksamples},
comparing each control group to its respective Landslide users group.
Anderson-Darling uses a weighted sum-of-squares distance metric to compare two CDFs,
testing if their samples are likely to arise from the same underlying, though unspecified, distribution%
\footnote{
I choose Anderson-Darling over the simpler Kolmogorov-Smirnov,
which computes only the maximum instantaneous distance between CDFs,
for its better sensitivity both to repeated deviations and to tail differences \cite{beware-kolmogorov-smirnov}.
}.
I deem the difference in grade distributions significant when $p < 0.05$%
% FIXME: is this legit?
% should you be using the combined/grouped AD test instead?
\footnote{I choose not to correct for multiplicity among these 4 comparsons (see next section)
because each one is testing a different hypothesis.
},
although as in all $p$-value calculations,
this rejects only the null hypothesis,
not alternative hypotheses (such as ``more skilled students were more likely to sign up to begin with'').

Ultimately, only the same-semester comparisons were significant
However, the distribution difference being smaller in P3 than in P2
% TODO: is there a good way to treat this more formally?
further suggests, albeit informally,
that the larger impact in P2 is not attributable {\em only} to selection bias.
% let me have this exclamation mark. please
That aside, ``Landslide helps students submit better P2s'' is the next most likely hypothesis I can think of!

@@

\begin{figure}[t]
	\begin{center}
		\small
	\begin{tabular}{cr|r||r|r|r|r||cc}
					&	&	&	&	& \multicolumn{2}{c}{Significance}
		\multicolumn{2}{c|}{Population}
					& $N$	& min	& mean	& max	& stddev & $p$ vs users	& cutoff\\
		\hline
			& users		& 103	& 42	& 74.8	& 95	& 10.3	& --	& --	\\
		P2	& non-users	& 74	& 38	& 70.9	& 96	& 12.5	& 0.036	& 0.05	\\
			& pre-study	& 86	& 43	& 73.7	& 93	& 9.7	& 0.671	& 0.05	\\
			\hline
			& users		& 98	& 65	& 83.6	& 95	& 6.2	& --	& --	\\
		P3	& non-users	& 63	& 45	& 80.7	& 93	& 8.2	& 0.034	& 0.05	\\
			& pre-study	& 79	& 60	& 81.6	& 95	& 7.6	& 0.145	& 0.05	\\
	\end{tabular}
	\end{center}
	\caption{Detailed statistics from student grade distributions.}
	\label{tab:table-of-ze-studence}
\end{figure}

@@

Human subjects research is inherently messy.
Each of the previous section's approaches to evaluating Landslide's educational value
was accompanied by some drawback which prevented it from being perfectly objective science,
but many of them presented tentatively positive results nonetheless.
Landslide helped many students find and fix many bugs (\sect{\ref{sec:education-eval-bugfinding}}),
but making a direct comparison to stress testing, the prior state of the art, is not straightforward.
Little, if any,
%and not statistically significant,
immediate improvement in students' project grades was measured
(\sect{\ref{sec:education-eval-grades}}),
but impact on grades alone is a very narrow measure of pedagogical value.
Landslide's debugging power was also found to be statistically significant
for the {\tt thr\_exit\_join} bug in particular, even after adjusting for multiplicity.
Students responded overwhelmingly positively in the survey (\sect{\ref{sec:education-eval-survey}}),
although it is easy to imagine students being equally happy with a ``debugging tool'' that just tells them all the answers.

>>>>

{\bf Statistical significance.}
Table~\ref{tab:table-of-ze-studence} presents more detailed statistics from these six distributions.
To assess whether the differences are significant,
% discrete == I used "version 2" of the AD metric that R outputs.
I use the $k$-sample discrete Anderson-Darling test \cite{anderson-darling}
provided by the R statistical programming environment \cite{r-lang,r-ksamples},
comparing each control group to its respective Landslide users group.
Anderson-Darling uses a weighted sum-of-squares distance metric to compare two CDFs,
testing if their samples are likely to arise from the same underlying, though unspecified, distribution%
\footnote{
I choose Anderson-Darling over the simpler Kolmogorov-Smirnov,
which computes only the maximum instantaneous distance between CDFs,
for its better sensitivity both to repeated deviations and to tail differences \cite{beware-kolmogorov-smirnov}.
}.
I deem the difference in grade distributions significant when $p < 0.05$%
% FIXME: is this legit?
% should you be using the combined/grouped AD test instead?
\footnote{I choose not to correct for multiplicity among these 4 comparsons (see next section)
because each one is testing a different hypothesis.
},
although as in all $p$-value calculations,
this rejects only the null hypothesis,
not alternative hypotheses (such as ``more skilled students were more likely to sign up to begin with'').
%
Ultimately, only the same-semester comparisons were significant.
However, the distribution difference being smaller in P3 than in P2
% TODO: is there a good way to treat this more formally?
further suggests, albeit informally,
that the larger impact in P2 is not attributable {\em only} to selection bias.
% let me have this exclamation mark. please
That aside, ``Landslide helps students submit better P2s'' is the next most likely hypothesis I can think of!

@@

% TODO: should i report the T.AD test statistic? i don't even know what it means lol but it's what the p value like, applies to..
\begin{figure}[t]
	\begin{center}
		\small
	\begin{tabular}{cr|r||r|r|r|r||cc}
		\multicolumn{3}{c||}{Population} & \multicolumn{4}{c||}{Distribution} & \multicolumn{2}{c}{Significance} \\
		project	& group		& $N$	& min	& mean	& max	& stddev & $p$ vs users	& cutoff\\
		\hline
			& users		& 103	& 42	& 74.8	& 95	& 10.3	& --	& --	\\
		P2	& non-users	& 74	& 38	& 70.9	& 96	& 12.5	& 0.036	& 0.05	\\
			& pre-study	& 86	& 43	& 73.7	& 93	& 9.7	& 0.671	& 0.05	\\
			\hline
			& users		& 98	& 65	& 83.6	& 95	& 6.2	& --	& --	\\
		P3	& non-users	& 63	& 45	& 80.7	& 93	& 8.2	& 0.034	& 0.05	\\
			& pre-study	& 79	& 60	& 81.6	& 95	& 7.6	& 0.145	& 0.05	\\
	\end{tabular}
	\end{center}
	\caption{Detailed statistics from student grade distributions.}
	\label{tab:table-of-ze-studence}
\end{figure}

@@

Human subjects research is inherently messy.
Each of the previous section's approaches to evaluating Landslide's educational value
was accompanied by some drawback which prevented it from being perfectly objective science,
but many of them presented tentatively positive results nonetheless.
Landslide helped many students find and fix many bugs (\sect{\ref{sec:education-eval-bugfinding}}),
but making a direct comparison to stress testing, the prior state of the art, is not straightforward.
%and not statistically significant,
Modest immediate improvement in students' project grades was observed,
(\sect{\ref{sec:education-eval-grades}}),
although statistical significance was lost when attempting to account for selection bias;
and impact on grades alone is a very narrow measure of pedagogical value anyway.
Landslide's debugging power was also found to be statistically significant
for the {\tt thr\_exit\_join} bug in particular, even after adjusting for multiplicity.
Students responded overwhelmingly positively in the survey (\sect{\ref{sec:education-eval-survey}}),
although it is easy to imagine students being equally happy with a ``debugging tool'' that just tells them all the answers.
